---
title: MeasurementOrFact statistics
author: Pieter Provoost
output: html_document
editor_options: 
  chunk_output_type: console
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "web") })    
---

```{r echo = FALSE, warning = FALSE, message = FALSE, results = 'asis'}
p(format(Sys.time(), "%B %d, %Y %H:%M"))
force_refresh <- TRUE
```

This is an overview of all OBIS datasets with (Extended)MeasurentOrFact records.

The **columns marked in green or blue** indicate the fraction of records that have a value for measurementType, measurementValue, measurementUnit, measurementTypeID, measurementValueID, and measurementUnitID.

The **last three columns** contain estimates of the fraction of missing values:

- **Missing measurementTypeID**: this is the number of records without a measurementTypeID relative to the total number of records, as every record is expected to have a measurementTypeID.
- **Missing measurementValueID**: this is the number of records without a measurementValueID relative to the number of records with a non numeric measurementValue. 
- **Missing measurementUnitID**: this is the number of records without a measurementUnitID relative to the number of records with a measurementUnit.

```{css, echo=FALSE}
p {
  margin: 10px 0px;
}
h3 {
  margin: 20px 0px;
}
```

```{r echo = FALSE, warning = FALSE, message = FALSE, results = 'asis'}
library(RPostgreSQL)
library(readr)
library(dplyr)
library(formattable)
library(htmltools)
library(stringr)

if (force_refresh == TRUE | !file.exists("stats.dat")) {
  readRenviron("env.txt")
  query <- read_file("query.sql")
  con <- dbConnect(RPostgres::Postgres(), dbname = Sys.getenv("OBIS_DB"), host = Sys.getenv("OBIS_HOST"), port = Sys.getenv("OBIS_PORT"), user = Sys.getenv("OBIS_USER"), password = Sys.getenv("OBIS_PASSWORD"), bigint = "integer")
  res <- dbSendQuery(con, query)
  stats <- fetch(res, n = -1)
  dbDisconnect(con)
  save(stats, file = "stats.dat")
} else {
  load("stats.dat")
}

stats <- stats %>%
  mutate(
    typeid_missing = ifelse(count > 0, round(typeid_missing / count, 2), 0),
    valueid_missing = ifelse(valueid_required > 0, round(valueid_missing / valueid_required, 2), 0),
    unitid_missing = ifelse(unit > 0, round(unitid_missing / unit, 2), 0)
  ) %>%
  mutate(
    type = round(type / count, 2),
    typeid = round(typeid / count, 2),
    value = round(value / count, 2),
    valueid = round(valueid / count, 2),
    unit = round(unit / count, 2),
    unitid = round(unitid / count, 2)
  ) %>%
  mutate(
    title = paste0("<a href=\"https://obis.org/dataset/", dataset_id, "\" target=\"_blank\">", title, "</a>")
  ) %>%
  select(title, node, records = count, type, value, unit, typeid, valueid, unitid, typeid_missing, valueid_missing, unitid_missing)

h3("Nodes")

tags$ul(tagList(lapply(unique(stats$node), function(n) {
  tags$li(a(n, href = paste0("#", str_replace(tolower(n), " ", "-"))))
})))

tagList(lapply(unique(stats$node), function(n) {
  
  subset <- which(stats$node == n)
  
  ft <- formattable(stats[subset,] %>% select(-node), list(
    type = x ~ color_tile("white", "darkolivegreen3")(stats$type)[subset],
    value = x ~ color_tile("white", "darkolivegreen3")(stats$value)[subset],
    unit = x ~ color_tile("white", "darkolivegreen3")(stats$unit)[subset],
    typeid = x ~ color_tile("white", "lightblue3")(stats$typeid)[subset],
    valueid = x ~ color_tile("white", "lightblue3")(stats$valueid)[subset],
    unitid = x ~ color_tile("white", "lightblue3")(stats$unitid)[subset],
    typeid_missing = x ~ color_tile("white", "orange")(stats$typeid_missing)[subset],
    valueid_missing = x ~ color_tile("white", "orange")(stats$valueid_missing)[subset],
    unitid_missing = x ~ color_tile("white", "orange")(stats$unitid_missing)[subset]
  ))
  rownames(ft) <- c()
  
  tagList(
    a(name = str_replace(tolower(n), " ", "-")),
    h3(n),
    as.htmlwidget(ft)
  )
  
}))
```

